### 2017-11-05 poster/poster.tex
finished

\usepackage{multicol} % This is so we can have multiple columns of text side-by-side
\columnsep=100pt % This is the amount of white space between the columns in the poster
\columnseprule=3pt % This is the thickness of the black line between the columns in the poster

@@

\begin{minipage}[b]{1\linewidth}
\veryHuge \color{NavyBlue} \textbf{Vertical and Oblique Transmission under Fluctuating Selection} \color{Black}\\ % Title
%\veryHuge \color{NavyBlue} \textbf{\qquad\qquad\qquad\qquad under Fluctuating Selection}\\[1cm] % Subtitle
\huge \textbf{Yoav Ram$^1,a$, Uri Liberman$^{2}$, and Marcus W. Feldman$^1$}\\ % Author(s)
\huge $^1$Department of Biology, Stanford University\\ % University/organization
\huge $^{2}$School of Mathematical Sciences, Tel-Aviv University\\ % University/organization
\huge $^{a}$yoav@yoavram.com\\ % Email
\end{minipage}
%
%\begin{minipage}[b]{0.25\linewidth}
%\color{DarkSlateGray}\Large \textbf{Contact Information:}\\
%Phone: +1 (650) 440-9625\\ % Phone number
%Email: \texttt{yoav@yoavram.com}\\ % Email address
%Twitter: \texttt{@yoavram}\\ % Twitter handle
%\end{minipage}
%%
%\begin{minipage}[b]{0.19\linewidth}
%\includegraphics[width=20cm]{cehg_logo} % Logo or a photo of you, adjust its dimensions here
%\end{minipage}

\vspace{1cm} % A bit of extra whitespace between the header and poster content

@@

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\color{Navy} % SaddleBrown color for the introduction

@@

%----------------------------------------------------------------------------------------
%	MODEL
%----------------------------------------------------------------------------------------

\color{DarkSlateGray} % DarkSlateGray color for the rest of the content

@@

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------

\section*{Results: Constant environment}

When the environment is constant, the fitness parameters $w_A$ and $w_B$ do not change between generations, and we have the following result.

\paragraph*{Result 1.} \textit{If $0<\rho\le 1$ and both $w_A$ and $w_B$ are positive with $w_A\ne w_B$, then fixation in the phenotype $A\ (B)$ is globally stable when $w_A>w_B$ $(w_A<w_B)$.}

\section*{Results: Periodically changing environment}

Consider an environmental regime $AkBl$ which favors phenotype $A$ for $k$ generations and then phenotypes $B$ for $l$ generations.
Let $W$ be the fitness of the favored phenotype and $w$ be that of the other phenotype where $0<w<W$.

\paragraph*{Result 2.}\textit{Fixation of both $A$ and $B$ is unstable if
\begin{equation}
-{\log(b)\over\log a} < {l \over k} < -{\log a\over\log(b)}.
\end{equation} 
Specifically, if $k=l$ then there is a protected polymorphism.}

@@

\paragraph*{Result 3.}\textit{In the case $A1B1$ with there exists a unique stable polymorphism:
\begin{equation}
x^* ={1\over 2} -{W+w-\sqrt{\left(1-\rho\right)^2\left(W-w\right)^2 +4Ww}\over 2\cdot(2-\rho)(W-w)}.
\end{equation}
}

@@

%\begin{center}\vspace{1cm}
%\begin{tabular}{l l l l}
%\toprule
%\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2} \\
%\midrule
%Treatment 1 & 0.0003262 & 0.562 \\
%Treatment 2 & 0.0015681 & 0.910 \\
%Treatment 3 & 0.0009271 & 0.296 \\
%\bottomrule
%\end{tabular}
%\captionof{table}{\color{Green} Table caption}
%\end{center}\vspace{1cm}

@@

Consider a modifier locus with alleles $m/M$ that determines the vertical transmission rates $\rho/P$:

\begin{equation}
\begin{matrix}
 \text{ pheno-genotype}&mA&mB&MA&MB\\
 \text{ frequency}&x_1&x_2&x_3&x_4\\
 \text{ fitness}&w_A&w_B&w_A&w_B\\
 \text{ vertical transmission rate}&\rho&\rho&P&P\\
\end{matrix}
\end{equation}

\section*{Results: $A1B1$ selection regime}

\paragraph*{Result 4.}\textit{In $A1B1$ selection regime, a modifier allele $m$ producing vertical transmission rate $\rho$ is stable to the introduction of a modifier allele $M$ with associated rate $P$ if $P>\rho$, and it is unstable if $P<\rho$.
}

@@

\section*{Results: $AkBl$ selection regime}

@@

@@

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\nocite{*} % Print all references regardless of whether they were cited in the poster or not
\bibliographystyle{plain} % Plain referencing style
\bibliography{sample} % Use the example bibliography file sample.bib

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\section*{Acknowledgements}

Partial support by the Stanford Center for Computational, Evolutionary and Human Genomics

>>>>

\usepackage{multicol} % This is so we can have multiple columns of text side-by-side
\columnsep=100pt % This is the amount of white space between the columns in the poster
\columnseprule=3pt % This is the thickness of the black line between the columns in the poster
%\raggedcolumns

@@

\begin{minipage}[b]{1\linewidth}

\center \veryHuge \color{NavyBlue} \textbf{Vertical and Oblique Transmission under Fluctuating Selection} \color{Black}\\ % Title

\vspace{1cm}

\huge \textbf{Yoav Ram$^{1,a}$, Uri Liberman$^{2}$, and Marcus W. Feldman$^1$}\\ % Author(s)

\vspace{1cm}

\huge $^1$ Department of Biology, Stanford University\\ % University/organization
\huge $^{2}$ School of Mathematical Sciences, Tel-Aviv University\\ % University/organization
%\huge $^{a}$yoav@yoavram.com\\ % Email

\vspace{1cm}

\Large $^{a}$ Postdoctoral fellow of the Stanford Center for Computational, Evolutionary and Human Genomics

\end{minipage}
%
%\begin{minipage}[b]{0.25\linewidth}
%\color{DarkSlateGray}\Large \textbf{Contact Information:}\\
%Phone: +1 (650) 440-9625\\ % Phone number
%Email: \texttt{yoav@yoavram.com}\\ % Email address
%Twitter: \texttt{@yoavram}\\ % Twitter handle
%\end{minipage}
%%
%\begin{minipage}[b]{0.2\linewidth}
%\includegraphics[width=0.5\linewidth]{avatar_150x225} % Logo or a photo of you, adjust its dimensions here
%\end{minipage}

\vspace{4cm} % A bit of extra whitespace between the header and poster content

@@

% INTRODUCTION

\color{DarkSlateGray}

@@

% MODEL

@@

We consider an environmental regime $AkBl$ which favors phenotype $A$ for $k$ generations and then phenotypes $B$ for $l$ generations.
Let $W$ be the fitness of the favored phenotype and $w$ be that of the other phenotype where $0<w<W$.

%\section*{Constant environment}
%
%When the environment is constant, the fitness parameters $w_A$ and $w_B$ do not change between generations, and we have the following result.
%
%\paragraph*{Result 1.} \textit{If $0<\rho\le 1$ and both $w_A$ and $w_B$ are positive with $w_A\ne w_B$, then fixation in the phenotype $A\ (B)$ is globally stable when $w_A>w_B$ $(w_A<w_B)$.}

\section*{Phenotype dynamics: $AkBl$}

\paragraph*{Result 1.}\textit{Fixation of both $A$ and $B$ is unstable if
\begin{equation}
\frac{\log a}{\log(b)} < \frac{l}{k} < \frac{\log(b)}{\log a}.
\end{equation} 
Specifically, if $k=l$ then there is a protected polymorphism.}

@@

\columnbreak

\section*{Phenotype dynamics: $A1B1$}

\paragraph*{Result 2.}\textit{In the case $A1B1$ with there exists a unique stable polymorphism:
\begin{equation}
x^* =\frac{1}{2} -\frac{W+w-\sqrt{\left(1-\rho\right)^2\left(W-w\right)^2 +4Ww}}{2\cdot(2-\rho)(W-w)}.
\end{equation}
}

@@

@@

Consider a modifier locus with alleles $m/M$ that determines the vertical transmission rates $\rho/P$:
\begin{equation}
\begin{matrix}
 \text{ pheno-genotype}&mA&mB&MA&MB\\
 \text{ frequency}&x_1&x_2&x_3&x_4\\
 \text{ fitness}&w_A&w_B&w_A&w_B\\
 \text{ vertical transmission rate}&\rho&\rho&P&P\\
\end{matrix}
\end{equation}

The next generation pheno-genotype frequencies are
\begin{equation}
\begin{aligned}
\hat{w}x'_1 &= w_A x_1\bigl[(1-\rho)(x_1+x_3) +\rho\bigr] +w_B x_2(1-\rho)(x_1+x_3)\\
\hat{w}x'_2 &= w_A x_1(1-\rho)(x_2+x_4) +w_B x_2\bigl[(1-\rho)(x_2+x_4)+\rho\bigr]\\ 
\hat{w}x'_3 &= w_A x_3\bigl[(1-P)(x_1+x_3) +P\bigr] +w_B x_4(1-P)(x_1+x_3)\\
\hat{w}x'_4 &= w_A x_3(1-P)(x_2+x_4) +w_B x_4\bigl[(1-P)(x_2+x_4)+P\bigr], 
\end{aligned}
\end{equation}

\paragraph{Evolutionary stable vertical transmission rate.}
We start with a single modifier $m$ with rate $\rho$ at equilibrium between phenotypes $A$ and $B$, and then introduce modifier $M$ with rate $P$ at a low frequency.
If $m$ is stable to invasion of every $M$ with any rate $P$, then we declare $\rho$ to be the stable rate $\rho^*$.

\columnbreak

\section*{Modifier dynamics: $A1B1$}

\paragraph*{Result 3.}\textit{In $A1B1$ selection regime, a modifier allele $m$ producing vertical transmission rate $\rho$ is stable to the introduction of a modifier allele $M$ with associated rate $P$ if $P>\rho$, and it is unstable if $P<\rho$.
}

Similar dynamics were observed in environments which randomly flip between $A$ and $B$ every generation.

@@

\columnbreak

\section*{Modifier dynamics: $AkBl$}

In the general case there is no reduction of the transmission rate, nor is there maximization of the population mean fitness.

@@

For $k \ne l$, there is a polymorphism between $A$ and $B$ for $w=0.1$ (but not $w=0.5$ or $0.9$), in which case the stable and optimal rates given in the table.

\begin{center}\vspace{1cm}
\begin{tabular}{p{2.5cm} p{2.5cm} p{4.5cm} p{4.5cm}}
\toprule
\textbf{$k$} & \textbf{$l$ } & \textbf{$\hat{\rho}$} & \textbf{$\rho^*$} \\
\midrule
1 & 2 & 0.00065 & 0.821 \\
3 & 10 & 0.00031 & 0.619 \\
5 & 30 & 0.00027 & 0.6503 \\
\bottomrule
\end{tabular}
\captionof{table}{Values of $\rho^*$ (stable rate) and $\hat\rho$ (fitness optimal rate) in $AkBl$ selection regime.}
\end{center}\vspace{1cm}

% Conclusions

@@

% REFERENCES

%\nocite{*} % Print all references regardless of whether they were cited in the poster or not
%\bibliographystyle{plain} % Plain referencing style
%\bibliography{sample} % Use the example bibliography file sample.bib
